Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-02 main.Rmd
wickets labels and facet label "innings" changed

```{r quasi-circular-example, echo = FALSE, out.width = "100%",fig.cap="
Terminology and intuition of quasi-circular granularities are shown. Panel a shows the time domain distributed as linear granularities $B$ (bottom granularity), $G$, $H'$ and quasi-circular granularities $Q(B, G)$ and $Q(B, H')$. Both $Q(B, G)$ and $Q(B, H')$ have repeating patterns unlike $G$ or $H'$ and the patterns are guided by the distribution of $B$ within $G$ and $H'$ and remains constant within a period shown by the hashed arrows. Panel b depicts the intuition through a measuring tape analogy where the folds are not of same length but has same length over a period."}
knitr::include_graphics("Figs/quasi-circular-ex2.png")
```

@@

cust2_box <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot"
  ) +
  scale_y_sqrt() +
  #ggtitle(" (a) Box plot faceted by hour-of-day") +
  xlab("") +
  ggtitle("") + ylab("") + 
  scale_x_discrete(labels = c('wdy','wnd'))

@@

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("inning:", inning)) %>% 
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) + 
  scale_fill_brewer(palette = "Dark2") + 
  #ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("a") +
  ylab("runs per over") +
  xlab("overs of the innings") +
  theme(plot.title = element_text(face = "bold"))
  # ggplot2::theme(
  #     strip.text = ggplot2::element_text(
  #       size = 7,
  #       margin = ggplot2::margin()
  #     )
  #   ) 
  #

@@

cricket_data <- cricket_tsibble %>%
  mutate(
    field = if_else(fielding_wckts == 0, "0 wicket", ">0 wickets"),
    dot = if_else(dot_balls == 0, "no dot balls", ">0 dot balls"),
    lag_field = lag(field),
    lag_dot = lag(dot)
  ) %>%
  filter(lag_field != 0, lag_dot != 0)

cricket_data$lag_field <- factor(cricket_data$field, levels = c("0 wicket", ">0 wickets"))

>>>>

```{r quasi-circular-example, echo = FALSE, out.width = "100%",fig.cap="Terminology and intuition of quasi-circular granularities are shown. Panel a shows the time domain distributed as linear granularities $B$ (bottom granularity), $G$, $H'$ and quasi-circular granularities $Q(B, G)$ and $Q(B, H')$. Both $Q(B, G)$ and $Q(B, H')$ have repeating patterns unlike $G$ or $H'$ and the patterns are guided by the distribution of $B$ within $G$ and $H'$ and remains constant within a period shown by the hashed arrows. Panel b depicts the intuition through a measuring tape analogy where the folds are not of same length but has same length over a period."}

knitr::include_graphics("Figs/quasi-circular-ex2.png")
```

@@

cust2_box <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot"
  ) +
  scale_y_sqrt() +
  #ggtitle(" (a) Box plot faceted by hour-of-day") +
  xlab("") +
  ggtitle("") + ylab("") + 
  scale_x_discrete(labels = c('wday','wend')) +
  ggplot2::theme(axis.text.x = element_text(size = 7))

@@

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("innings: ", inning)) %>% 
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) + 
  scale_fill_brewer(palette = "Dark2") + 
  #ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("a") +
  ylab("runs per over") +
  xlab("overs of the innings") +
  theme(plot.title = element_text(face = "bold")) +
  ggplot2::theme(
       strip.text = ggplot2::element_text(
        size = 10,
         margin = ggplot2::margin(b=0, t=0)
      )
     )

@@

cricket_data <- cricket_tsibble %>%
  mutate(
    field = if_else(fielding_wckts == 0, "0", "1+"),
    dot = if_else(dot_balls == 0, "no dot balls", ">0 dot balls"),
    lag_field = lag(field),
    lag_dot = lag(dot)
  ) %>%
  filter(lag_field != 0, lag_dot != 0)

cricket_data$lag_field <- factor(cricket_data$field, levels = c("0", "1+"))
